\documentclass[letterpaper, 10pt]{article}

\usepackage{titlesec}
\usepackage{titling}
\usepackage[margin=0.75in]{geometry}
\usepackage{multicol}
\usepackage{enumitem}

\setenumerate{nolistsep}
%\setitemize{nolistsep}

\titleformat{\section}
{\large\bfseries\uppercase}
{}
{0em}
{}[\titlerule]

\titleformat{\subsection}
{\large\bfseries}
{}
{0em}
{}

\titleformat{\subsubsection}[runin]
{\bfseries}
{}
{0em}
{}[:]

\titlespacing{\section}
{0em}{1.5em}{0.5em}

\titlespacing{\subsection}
{0em}{0em}{0.25em}

\titlespacing{\subsubsection}
{1em}{0.5em}{0.5em}

\renewcommand{\maketitle}
{\begin{center}
{\Large\bfseries\MakeUppercase\theauthor}

chrislavoy@gmail.com\\
602\--999\--2734
\end{center}
}

\begin{document}

\author{Chris LaVoy}

\maketitle

\vspace{-1.5em}
\begin{center}
\em Seeking a full time entry level Software Engineering position.
\end{center}

\vspace{-2em}

\section{Education}

\subsection{Arizona State University}

Bachelors of Science in Computer Science (August 2018)

Computer Gaming Certificate (Completed May 2015)

\vspace{-0.5em}
\section{Experience}

\subsection{Software Engineer, Lighthouse Document Technologies (2018 \- Present)}
\begin{itemize}
\setlength\itemsep{-0.25em}
\item Work with a team of developers in an agile environment on an eDiscovery platform as a service
\item Design and implement features across front and back end of our application
\item Support our application in production and document the process to help onboard new developers
\end{itemize}

\subsection{Software Engineering Intern, THE MEME Design (Summer 2016)}
\begin{itemize}
\setlength\itemsep{-0.25em}
\item Worked in a startup environment, creating web services and web applications for customers.
\item Led client meetings to discuss product requirements and present work completed for client approval.
\item Led a small team of developers and designers creating a web application.
\end{itemize}

\subsection{Student Web/Mobile Developer, Arizona State University (2014 \-- 2017)}
\begin{itemize}
\setlength\itemsep{-0.25em}
\item Created and maintained web and mobile applications using JavaScript.
\item Wrote automation and utility scripts to improve workflow.
\item Explored the possibilities of the Internet of Things and various technologies on the Arizona State University campus.
\end{itemize}

\subsection{Game Camp Teaching Assistant, Arizona State University (Summer 2015)}
\begin{itemize}
\setlength\itemsep{-0.25em}
\item Helped students understand the process of creating games.
\item Assisted students with writing and troubleshooting code.
\item Inspired the next generation of students to explore their creativity, expand their technical skills.
\end{itemize}

\subsection{Technology Consultant Lead, Arizona State University (2011 \-- 2014)}
\begin{itemize}
\setlength\itemsep{-0.25em}
\item Resolved various classroom technology issues, including software, hardware, and audio/visual equipment.
\item Installed and maintained classroom technology and computer software including system images and various applications.
\end{itemize}

\subsection{Related Projects}

\subsubsection{Simulation Tool Kit}
\hangindent2em Created a modular toolkit for rapid development of a city traffic simulation, including pedestrian, car, and train traffic agents. (C\#, Unity3D)

\subsubsection{MapBuilder}
\hangindent2em Collaborated on a web form and map widget that generates code to insert a customized map view on an ASU webpage. (HTML, CSS, JavaScript, PHP)

\subsubsection{Stadium Noise Game}
\hangindent2em Designed a web application that displays sound levels on the jumbotron in Sun Devil Stadium, encouraging the audience to cheer and be the loudest section. (HTML, CSS, SVG, JavaScript)

\vspace{-0.5em}

\section{Skills}

\subsection{Languages}
\vspace{-1em}
\begin{multicols}{2}
\subsubsection{Programming}

C, C++, Go, JavaScript, C\#, Java

\subsubsection{Markup}

HTML, CSS, {\LaTeX}
\end{multicols}
\vspace{-0.5em}

\subsection{Tools}

Vim, Git, Unity3D, XNA, Visual Studio, VS Code, Atom, Linux, macOS, Windows, MySQL, Microsoft Office

\vspace{0.5em}
\subsection{Additional Skills}
\vspace{-1.25em}
\begin{multicols}{2}
\begin{itemize}[nolistsep]
%\setlength\itemsep{-0.25em}
\item Basic working proficiency in Mandarin Chinese.
\item Experience leading teams of people.
\item Excellent verbal and written communication skills.
\item Ability to work independently or as part of a team.
\item Strong drive and interest in learning new things.
\end{itemize}
\end{multicols}

\end{document}
