\documentclass[letterpaper, 10pt]{article}

\usepackage{titlesec}
\usepackage{titling}
\usepackage[margin=0.75in]{geometry}
\usepackage{multicol}

\titleformat{\section}
{\Large\bfseries}
{}
{0em}
{}[\titlerule]

\titleformat{\subsection}
{\large\bfseries}
{}
{0em}
{}

\titleformat{\subsubsection}[runin]
{\bfseries}
{}
{0em}
{}[:]

\titlespacing{\subsection}
{0em}{.5em}{0.25em}

\titlespacing{\subsubsection}
{1em}{0.5em}{0.5em}

\renewcommand{\maketitle}
{\begin{center}
{\Large\bfseries
\theauthor}

chrislavoy@gmail.com\\
602\--999\--2734
\end{center}
}

\begin{document}

\author{Chris LaVoy}

\maketitle

\vspace{-2em}
\begin{center}
\em Seeking a full time entry level Software Engineering position.
\end{center}

\vspace{-2em}

\section{Education}

\subsection{Arizona State University}

Bachelors of Science in Computer Science, Computer Gaming Certificate (Expected May 2018)
\\
\\
\textbf{Courses Completed}
\vspace{-1em}
\begin{multicols}{2}
\begin{itemize}
\setlength\itemsep{-0.25em}
\item Object-Oriented Programming
\item Assembly Language Programming
\item Introduction to Programming Languages
\item Data Structures and Algorithms
\item Introduction to Software Engineering
\item Theoretical Computer Science
\item Operating Systems
\item Principles of Programming Languages
\item Visualization and Simulation in Japan
\item Game Engine Development
\item Gaming Capstone
\item Graphics for Games
\end{itemize}
\end{multicols}

\section{Experience}

\subsection{Software Engineering Intern, THE MEME inc. (Summer 2016)}
\begin{itemize}
\setlength\itemsep{-0.25em}
\item Worked in a startup environment, creating web services and web applications for customers.
\item Led client meetings to discuss product requirements and present work completed for client approval.
\item Led a small team of developers and designers creating a web application.
\end{itemize}

\subsection{Student Web/Mobile Developer, Arizona State University (2014 \-- 2017)}
\begin{itemize}
\setlength\itemsep{-0.25em}
\item Created and maintained web and mobile applications using JavaScript.
\item Wrote automation and utility scripts to improve workflow.
\item Explored the possibilities of the Internet of Things and various technologies on the Arizona State University campus.
\end{itemize}

\subsection{Technology Consultant Lead, Arizona State University (2011 \-- 2014)}
\begin{itemize}
\setlength\itemsep{-0.25em}
\item Resolved various classroom technology issues, including software, hardware, and audio/visual equipment.
\item Installed and maintained classroom technology and computer software including system images and various applications.
\end{itemize}

\section{Technical Skills}

\subsection{Languages}

\subsubsection{Programming}

C, C++, Go, JavaScript, C\#, Java

\subsubsection{Markup}

HTML, CSS, {\LaTeX}

\subsection{Projects}

\subsubsection{Simulation Tool Kit}
\hangindent2em Created a modular toolkit for rapid development of a city traffic simulation, including pedestrian, car, and train traffic agents. (C\#, Unity3D)

\subsubsection{MapBuilder}
\hangindent2em A web form and map widget that will generate code to insert a customized map view on an ASU webpage. (HTML, CSS, JavaScript, PHP)

\subsubsection{Stadium Noise Game}
\hangindent2em A web application that collects and displays live data from sound sensors in Sun Devil Stadium to encourage the audience to cheer and be the loudest section. (HTML, CSS, SVG, JavaScript)

\subsection{Tools}

Vim, Git, Unity3D, XNA, Visual Studio, VS Code, Atom

\section{Additional Skills}

\begin{itemize}	
\setlength\itemsep{-0.25em}
\item Basic working proficiency in Mandarin Chinese.
\item Excellent verbal and written communication skills.
\item Ability to work independently or as part of a team.
\item Experience leading teams of people.
\item Strong drive and interest in learning new things.
\end{itemize}

\end{document}
